### 2023-04-01 main/chapter_experiment.tex
begin lhc section; add complex figure

\section{Design}
Atlas is a Titan.
\atlas\ is the largest detector experiment at the LHC,
and alongside its biggest neighbours
\cms~\cite{cms2008experiment},
\lhcb~\cite{lhcb2008experiment},
and ALICE~\cite{alice2008experiment}
it is a multi-kilotonne beast,
and a wonder of scientific engineering~\cite{
atlas1994proposal,
atlas2008experiment,
atlas1999design1,
atlas1999design2
}.

>>>>

Without high-energy hadron collisions in its centre, \atlas\ would be neutered.
For all of our data, we are therefore indebted to the LHC for so reliably
providing these exciting particle interactions.
We therefore begin this chapter with a description of the LHC itself in
Section~\ref{sec:atlas_lhc} before detailing the design of \atlas\ in
Section~\ref{sec:atlas_design}.

\section{The Large Hadron Collider}
\label{sec:atlas_lhc}

% the LHC
% where the protons come from
Figure~\ref{fig:atlas_cern_complex}

\begin{figure}[tp]
\centering
\includegraphics[width=0.98\textwidth]{figures/atlas_lhc_complex.png}
\caption[
The CERN accelerator and detector complex, with the LHC as its largest piece
]{%
The CERN accelerator and detector complex, with the LHC as its largest piece
shown in dark blue-grey.
The complex uses a sequence of increasingly large and powerful accelerators to
boost ionised particles to their final collision energies in the LHC and to
yield beams for other CERN experiments.
This poster is adapted from~\cite{Haffner:1621894}.
}
\label{fig:atlas_cern_complex}
\end{figure}

% the accelerator complex
% RF cavities
% magnets (dipole, quadrupole etc)
% size of beam
% luminosity and its uncertainty
% pile-up

\section{Design}
\label{sec:atlas_design}
Atlas is a Titan.
\atlas\ is the largest detector experiment at the LHC,
and alongside its biggest neighbours
\cms~\cite{cms2008experiment},
\lhcb~\cite{lhcb2008experiment},
and ALICE~\cite{alice2008experiment}
it is a multi-kilotonne beast,
and a wonder of scientific engineering~\cite{
atlas1994proposal,
atlas2008experiment,
atlas1999design1,
atlas1999design2
}.
